### 2015-11-18 ch02-qlogms/excitation-design.tex
Fixup OE diagram

\subsection{System and noise model}
  In this chapter, an output error (OE) system setup is used.
  Denote
    $U  \left(\omega\right)$ as the excitation signal,
    $Y_0\left(\omega\right)$ the exact, unperturbed system output,
    $E  \left(\omega\right)$ for the output noise source,
    $Y  \left(\omega\right) = Y_0\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.

  \begin{figure}
    \centering
    \input{\thisDir/figs/oesetup.tikz}
    \caption[Output-error]{Output-error set-up.}
  \end{figure}

@@

  \TODO{put block diagram here}

>>>>

\subsection{System and noise model}
  In this chapter, an output error (OE) system setup is used.
  Denote
    $U  \left(\omega\right)$ as the excitation signal,
    $\true{Y}\left(\omega\right)$ the exact, unperturbed system output,
    $E  \left(\omega\right)$ for the output noise source,
    $Y  \left(\omega\right) = \true{Y}\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.

  \begin{figure}
    \centering
    \input{\thisDir/figs/oesetup.tikz}
    \caption[Output-error]{Output-error set-up.}
    \label{fig:excitation:OE}
  \end{figure}

@@
